Spin canonical divisors of log stacky curves

### 2015-06-28 stacky_write_up/spin_cring.tex
lemmata -> lemmas

%%%%%%%%%%%%%%%%%%%%%%%%%%% Inductive Lemmata %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Inductive Lemmata}
\label{sec:induction}
First we present several lemmata which provide the
inductive steps in the proof of the main theorem, Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
which describe the generators and relations of $R_{D + \frac{\alpha
}{\beta}P},$ given those in $R_D,$ 
where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
$D \in \di
X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ.$ 
In
Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log half canonical ring of a curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of a
curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. 
%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%half-canonical divisors, although even Lemma
%~\ref{lem:raise-stacky-order} has certain generalizations, as noted
%in Remark ~\ref{rem:raise-fractional-order}

%However, before we can answer these general Lemmata, it is useful
%to prove a nice result about minimal generation of ideals of
%relations.
%
%\todo{Include one of the following, if the first one, include a 
%remark for quotient}

@@

One can prove similar results in cases with different conditions on saturation, base-point freeness, and the coefficients of added points, but only these three cases (Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}) are needed for the remainder of this paper.  Instead we turn now to inductive methods to incrementally increase the $e_i$s.  Combined with the previous lemmata on adding points, these will provide all the necessary inductive tools for the remainder of the paper.

@@

\ssec{Saturation}
\label{ssec:g_0_saturation}
First, we present the saturations of the canonical divisor for
all cases where $g = 0$ and $\delta = 0,$ as defined in Definition
~\ref{defn:sat}. The saturations can be computed using Riemann-Roch.
By classifying the saturations of all signatures, we can determine
the base cases on which we can apply inductive lemmata from
Section ~\ref{sec:induction}. Exceptional cases are listed first
and generic cases follow.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%% Inductive lemmas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Inductive lemmas}
\label{sec:induction}
First we present several lemmas which provide the
inductive steps in the proof of the main theorem, Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
which describe the generators and relations of $R_{D + \frac{\alpha
}{\beta}P},$ given those in $R_D,$ 
where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
$D \in \di
X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ.$ 
In
Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log half canonical ring of a curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of a
curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. 
%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%half-canonical divisors, although even Lemma
%~\ref{lem:raise-stacky-order} has certain generalizations, as noted
%in Remark ~\ref{rem:raise-fractional-order}

%However, before we can answer these general lemmas, it is useful
%to prove a nice result about minimal generation of ideals of
%relations.
%
%\todo{Include one of the following, if the first one, include a 
%remark for quotient}

@@

One can prove similar results in cases with different conditions on saturation, base-point freeness, and the coefficients of added points, but only these three cases (Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}) are needed for the remainder of this paper.  Instead we turn now to inductive methods to incrementally increase the $e_i$s.  Combined with the previous lemmas on adding points, these will provide all the necessary inductive tools for the remainder of the paper.

@@

\ssec{Saturation}
\label{ssec:g_0_saturation}
First, we present the saturations of the canonical divisor for
all cases where $g = 0$ and $\delta = 0,$ as defined in Definition
~\ref{defn:sat}. The saturations can be computed using Riemann-Roch.
By classifying the saturations of all signatures, we can determine
the base cases on which we can apply inductive lemmas from
Section ~\ref{sec:induction}. Exceptional cases are listed first
and generic cases follow.
